\newacronym	{INSO}	{INSO}	{Industrial Software}
\newacronym	{TU}	{TU}	{Technische Universit\"at Wien}
\newacronym	{ZID}	{ZID}	{Zentraler Informatikdienst}
\newacronym	{KISS}	{KISS}	{Keep It Sober and Significant}
\newacronym	{APP}	{APP}	{Anwendungssoftware}
\newacronym	{GUI}	{GUI}	{Benutzeroberfläche}
\newacronym	{API}	{API}	{Programmierschnittstelle}
\newacronym	{TS}	{TS}	{TypeScript}
\newacronym	{JS}	{JS}	{JavaScript}
\newacronym	{ERM}	{ERM}	{Entity-Relationship-Modell}
\newacronym	{UML}	{UML}	{Unified Modeling Language}
\newacronym	{HTML}	{HTML}	{Hypertext Markup Language}
\newacronym	{CSS}	{CSS}	{Cascading Style Sheets}
\newacronym	{OS}	{OS}	{Betriebssystem}
\newacronym	{DBMS}	{DBMS}	{Datenbankmanagementsystem}
\newacronym	{DB}	{DB}	{Datenbank}
\newacronym	{SPA}	{SPA}	{Single Page Applikation}
\newacronym	{SPAs}	{SPAs}	{Single Page Applikationen}
\newacronym	{SQL}	{SQL}	{Structured Query Language}
\newacronym	{etc.}	{etc.}	{et cetera}
\newacronym	{bzw.}	{bzw.}	{beziehungsweise}
\newacronym	{usw.}	{usw.}	{und so weiter}
\newacronym	{AJAX}	{AJAX}	{Asynchronous JavaScript and XML}
\newacronym	{HTTP}	{HTTP}	{Hypertext Transfer Protocol}
\newacronym	{HTTPS}	{HTTPS}	{Hypertext Transfer Protocol Secure}
\newacronym	{PDF}	{PDF}	{Portable Document Format}
\newacronym	{SMTP}	{SMTP}	{Simple Mail Transfer Protocol}
\newacronym	{SVG}	{SVG}	{Scalable Vector Graphics}
\newacronym	{URI}	{URI}	{Uniform Resource Identifier}
\newacronym	{URL}	{URL}	{Uniform Resource Locator}
\newacronym	{WWW}	{WWW}	{World Wide Web}
\newacronym	{JSON}	{JSON}	{JavaScript Object Notation}
\newacronym	{z.B.}	{z.B.}	{zum Beispiel}
\newacronym	{DOM}	{DOM}	{Document Object Model}
\newacronym	{DGBL}	{DGBL}	{Digital game-based learning}
\newacronym	{EU}	{EU}	{Europäische Union}
\newacronym	{IT}	{IT}	{Informationstechnik}
\newacronym	{ER}	{ER}	{Entity-Relationship}
\newacronym	{VR}	{VR}	{Virtual Reality}
\newacronym	{SG}	{SG}	{Serious Game}
\newacronym	{ISO}	{ISO}	{International Organization for Standardization}
\newacronym {ROM}   {ROM}   {Range of Motion}
\newacronym {ca.}   {ca.}   {circa}

